---
name: Yangzhuoran Fin Yang
position: "PhD Student"
address: "Monash University, Australia"
phone: +61 414 060 712
www: yangzhuoranyang.com
email: "Fin.Yang@monash.edu"
twitter: YangzhuoranY
github: FinYang
linkedin: yangzhuoranyang
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
# library(RefManageR)
```

```{r Rpackages, eval=FALSE}
# Construct bib file for R packages
source("Rpackages.R")
write_packages_bib(
  pkglist = c("RRRR", 
              "tsfeatures",
              "Mcomp",
              "tscompdata", 
              "tsdl", 
              "stocon",
              "compenginets", 
              "lazytype", 
              "lazybar",
              "ycevo", 
              "demography"),
  file="Rpackages.bib")
```

# Education

```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Doctor of Philosophy in Statistics", 
  "Monash University", "Clayton, Australia", 
  "Apr. 2020 - Present", 
  "Forecast reconciliation with linear combinations",
  
  "Bachelor of Commerce (Hons) in Econometrics", 
  "Monash University", "Clayton, Australia", 
  "Feb. 2019 - Nov. 2019", 
  "Thesis: Optimal portfolio selection via dimensional reduction in a stochastic optimal control setting",
  
  "Bachelor of Commerce (Hons) in Econometrics", 
  "Monash University", 
  "Clayton, Australia", 
  "Feb. 2019 - Nov. 2019", 
  "GPA of 3.875, GRADE H1",
  
  "Bachelor of Actuarial Science", 
  "Monash University", 
  "Clayton, Australia", 
  "Jul. 2016 - Jul. 2018", 
  "GPA of 4, WAM of 90.323", 
  
  # "Bachelor of Finance",
  # "Henan University", 
  # "Kaifeng, China", 
  # "Sep. 2014 - Present", 
  # "GPA of 3.940"
) %>% 

  detailed_entries(degree, dates, uni, loc, details)

```

# Experience

```{r}

tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,

  "Visiting Student", 
  "ShanghaiTech University SIST",
  "Shanghai, China", 
  "Dec. 2019 - Aug. 2020", 
  "Supervisor: Professor Ziping Zhao",
  
  "Teaching Associate", 
  "Monash University", 
  "Clayton, Australia", 
  "Mar. 2019 - Present", 
  "Business and economic statistics (ETC1000)",

  "Teaching Associate", 
  "Monash University", 
  "Clayton, Australia", 
  "Mar. 2019 - Present", 
  "Applied econometrics (ETC3410)",
  
  "Research Assistant", 
  "Monash University", 
  "Clayton, Australia", 
  "Sep. 2017 - Present", 
  "Responsibilities including developments of R packages and data manipulation",
  
  "Research Assistant", 
  "Monash University", 
  "Clayton, Australia", 
  "Sep. 2017 - Present", 
  "Concepts involving time series, financial data, dimension reduction and stochastic optimization",
  
  "Research Assistant", 
  "Monash University", 
  "Clayton, Australia", 
  "Sep. 2017 - Present", 
  "Supervisors include Dr Bonsoo Koo, Dr Dan Zhu, and Professor Rob Hyndman",
  
  "Private tutor", 
  "Australia Ultimate Services", 
  "Clayton, Australia", 
  "Sep. 2017 - Jul. 2019", 
  "Introductory econometrics, Actuarial statistics, Probability and statistical inference for economics and business, Applied econometrics and Financial econometric",
  
  "Teaching Associate", 
  "Monash University", 
  "Clayton, Australia", 
  "Jul. 2017 - Nov. 2017", 
  "Introduction to financial accounting (ACC1100)",
  
  "Private tutor", 
  "HDEDU",
  "Clayton, Australia", 
  "Feb. 2017 - Sep. 2017", 
  "Introductory econometrics and Actuarial statistics"





) %>% 

  detailed_entries(role, dates, company, loc, details)

```

# Publications

```{r}
# pubs <- ReadBib("publications.bib", check = FALSE)
bibliography_entries("publications.bib") %>%
  arrange(year, surnames) %>% 
  `rownames<-`(NULL)
```


\pagebreak

# Awards

* 2019 Monash Business School Dean's Honour

<!-- * 2019 Monash Business School Co-funded Graduate Research Scholarship -->

* 2019 Monash University Econometrics Honours Memorial Scholarship

* 2018 Monash Business School Prize for the Top Achieving Student in Actuarial Science (Undergraduate) 

* 2018 Monash University Medal for Undergraduate Academic Excellence

* 2018 Monash Business School Dean's Honour

* 2018 Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:  

  - Business analytics
  - Modelling in finance and insurance
  - Applied forecasting for business and economics

* 2018 The International Institute of Forecasters Student Forecasting Award 
    offered by Monash University Applied Forecasting for Business and Economics 

* 2017 Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:  

  - Statistical Thinking
  - Principles of Econometrics
  - Contingencies in insurance and pensions
  
* 2016 Henan University Undergraduate Scholarship 

* 2016 Henan University Outstanding Student Award

```{r, eval = F}

tribble(
  ~ award, ~ from, ~ year, ~details,
  "Monash University Econometrics Honours Memorial Scholarship", "Monash", "2019", NA,
  "Monash Business School Prize for the Top Achieving Student in Actuarial Science (Undergraduate)", "Monash", "2018", NA,
  "Monash University Medal for Undergraduate Academic Excellence", "Monash", "2018", NA,
    "Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:", "Monash", "2018", "Business analytics", 
      "Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:", "Monash", "2018", "Modelling in finance and insurance", 
      "Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:", "Monash", "2018", "Applied forecasting for business and economics", 
  "The International Institute of Forecasters Student Forecasting Award o", "IIF", "2018", NA,
    "Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:", "Monash", "2017", "Statistical Thinking", 
      "Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:", "Monash", "2017", "Principles of Econometrics", 
      "Monash Business School Student Excellence Award in recognition of exceptional academic excellence in:", "Monash", "2017", "Contingencies in insurance and pensions"
) %>%
  brief_entries(gsub("NA", "", paste0(award, details)), year, from)

```


# Software (R packages)

R packages that I've contributed or co-authored.

```{r r-packages}
# Sort R packages by title, then year.
bibliography_entries("Rpackages.bib",
  startlabel = "packagestart", endlabel = "packageend"
) %>%
  arrange(title, year)
```


<!-- 

\pagebreak 

# Referees

```{r}
tribble(
  ~ name, ~ uni, ~ loc, ~ dates, ~ details,
  "Professor Rob J Hyndman", 
  "Monash University", "Professor", 
  "Clayton, Australia", 
  "Email: Rob.Hyndman@monash.edu",
  
  "Dr Dan Zhu", 
  "Monash University", "Senior Lecturer", 
  "Clayton, Australia", 
  "Email: Dan.Zhu@monash.edu",
  
  "Assoc Professor Bonsoo Koo", 
  "Monash University", "Associate Professor", 
  "Clayton, Australia", 
  "Email: Bonsoo.Koo@monash.edu",
  

) %>% 

  detailed_entries(loc, dates, name, uni, details)
```

-->